\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
more updates

Summary: the article describes the layout, operation and performances of a Radial Time Projection Chamber with the electron amplification stage provided by three layers of GEM. The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane. The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line. 
The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.
Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data. 
Chapter 2 focuses on the RTPC mechanical and electrical layout. From inner to outer, there are: the 4He gas target, a 4He gas gap, the actual time projection chamber. The time projection chamber is a 200 long detector composed by different gas gaps limited by concentric electrodes around the axis: cathode (R=30mm), G1(R=60mm), G2(R=63mm), G3(R=66mm), readout plane (R=69mm). Everything fits inside a 5T solenoidal magnetic field. It provides both time and charge measurements.
Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.
Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.
Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.
Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.

The article main points of interest are the followings:\\
a)  the usage of GEMs as avalanche creators inside the time projection chamber. As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.\\
b) The shaping of the GEM foils around the target. However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\
Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.
--------------------------------------------------

\section*{Chapter by chapter comments}:

>>>>

Summary: the article describes the layout, operation and performances of a Radial Time Projection Chamber with the electron amplification stage provided by three layers of GEM. The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane. The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line.\\

The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.\\

Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data.\\ 
Chapter 2 focuses on the RTPC mechanical and electrical layout. From inner to outer, there are: the 4He gas target, a 4He gas gap, the actual time projection chamber. The time projection chamber is a 200 long detector composed by different gas gaps limited by concentric electrodes around the axis: cathode (R=30mm), G1(R=60mm), G2(R=63mm), G3(R=66mm), readout plane (R=69mm). Everything fits inside a 5T solenoidal magnetic field. It provides both time and charge measurements.\\
Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.\\
Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.\\
Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.\\
Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.\\

The article main points of interest are the followings:\\
a)  the usage of GEMs as avalanche creators inside the time projection chamber. As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.\\
b) The shaping of the GEM foils around the target. However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\

Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.\\

Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.\\
--------------------------------------------------\\

\section*{Chapter by chapter comments}
